Customizing Software by Direct Manipulation of Structured Data

### 2020-05-20 paper.tex
latest draft

We have known for decades about an alternate approach: \emph{direct
manipulation} \citep{shneiderman1983}, where ``visibility of the object
of interest'' replaces ``complex command language syntax''. Direct
manipulation is the de facto standard in GUIs today, but when it comes
to customizing software, it is rarely to be found. In this work, we ask:
what would it look like to build a software customization interface that
deeply relies on direct manipulation? We take inspiration from
spreadsheets and visual database query interfaces
\citep{2020a, bakke2016}, which have successfully enabled end users to
construct queries, edit data, and compute derived values through direct
manipulation of structured data.

In this paper we present a technique called \emph{table-driven
customization} which applies these ideas from visual query interfaces in
the context of software customization. We augment an application's UI
with a table view, where the user can see and manipulate the structured
data inside an application. Changes in the table view result in
immediate corresponding changes to the original user interface of the
application, enabling the user to customize an application with live
feedback. The table view and the original UI serve as coordinated
\emph{multiple representations} of the same underlying state.

To demonstrate the viability of this approach, we have developed a
browser extension called Wildcard which implements table-driven
customization in the context of the Web. Wildcard is compatible with
existing unmodified applications because it uses web scraping techniques
to extract relevant state into a table and to reify changes in the
original application UI. In Section~\ref{sec:examples} we present a many
examples of using Wildcard to implement useful customizations across
real websites, ranging from sorting lists of data to adding whole new
features to applications.

In Section~\ref{sec:architecture} explain the \emph{table adapter}
abstraction, which allows many different types of underlying state to be
bidirectionally mapped to a table of data. We explore how table adapters
are general enough to support many customizations beyond the ones we've
built so far in Wildcard; we also discuss how applications could be
re-architected to expose tabular data directly to end users, rather than
relying on web scraping techniques.

In Section~\ref{sec:prototype} we discuss in more detail the
implementation of the Wildcard browser extension. We reflect on the
experience of using the tool to customize websites, and some of the
challenges from the perspective of programmers and end users.

Table-driven customization embodies several design principles for
building customizable software systems, discussed in
Section~\ref{sec:discussion}:

@@

@@

\begin{itemize}
\tightlist
\item
  basic idea: end user editing a table. but these edits have effects.
\item
  table adapter: component that presents an interface similar to a SQL
  table. but inside, it can do anything to produce that data, and can do
  anything with incoming edits.

  \begin{itemize}
  \tightlist
  \item
    out: table
  \item
    in: table
  \item
    in: other tables
  \end{itemize}
\end{itemize}

@@

The basic data unit in table-driven customization is a Table: an ordered
list of tuples, each of which has an ID and some attributes. The user
always sees a single table in the table editor, but this table is the
result of combining data across one or more underlying tables, much like
viewing the result of a SQL query across multiple database tables. Each
individual table's data is managed by a ``table adapter'' component, and
a query engine coordinates across the various table adapters.

(\emph{Todo: drive this explanation via concrete example. Add a
figure.}) For example, one table adapter manages scraping data from the
DOM of a site, while another manages extracting data from AJAX requests.
Each table adapter produces a table of data, and the two are joined
together by a shared ID column to produce what looks like a single table
of data extracted from the site. Similarly, when the user makes
annotations on a site, these annotations are handled by a third table
adapter, which manages a data table stored in the browser's local
storage.

\hypertarget{table-adapter-api}{%
\subsection{Table adapter API}\label{table-adapter-api}}

(\emph{Todo: formalize this more? Would math notation help?})

In order to promote uniformity within the system, we've defined a small
abstract API, which all table adapters conform to.

The main purpose of a table adapter is to return a table representing
some data source. The table is live-updating: a table adapter can
produce a new version of its data table at any point (e.g., updating the
data table in response to a change in a website's DOM). When this
happens the new data is pushed to the editor and the query results are
refreshed.

Table editors also accept various incoming commands.

The editor can request to a table adapter to make an edit to a record.
The meaning of making an edit can vary depending on the adapter: in the
local storage adapter, an annotation can be persisted into local
storage; in the DOM scraping adapter, an edit can represent filling in a
form field. An adapter can also mark values as read-only if it wouldn't
be meaningful to edit them; for example, the DOM scraping adapter
typically marks page content as read-only, except for editable form
fields.

The query engine also sends each table adapter information about the
entire cross-table query view being created by the user. This
functionality is currently mainly used by the DOM scraping adapter to
make changes to the original web page:

\begin{itemize}
\tightlist
\item
  observes the sort order of the query view to re-order rows in the page
\item
  observes the content of other joined tables to render annotations in
  the page
\item
  observes the currently selected row in the UI, to highlight the
  corresponding row in the page
\end{itemize}

@@

Here we describe in more detail the table adapters which we have
implemented to power the customizations shown above.

\textbf{DOM scraping adapters} are a key part of the Wildcard system.
These adapters extract data from the DOM of a web page, and manipulate
the DOM to re-order rows, edit form entries, and inject annotations. To
create a DOM scraping adapter for a specific website, a programmer does
not need to implement all this functionality from scratch. They only
need to write a single scraping function which uses CSS selectors and
DOM APIs to extract and return relevant elements. The Wildcard framework
then wraps this function to implement the rest of the needed
functionality.

(\emph{todo: get into the Sorting Problem? i.e., once we sort the page,
the original sort order is lost from the page. Maybe not
necessary\ldots{}})

\hypertarget{other-table-adapters}{%
\subsection{Other table adapters}\label{other-table-adapters}}

An \textbf{AJAX scraping adapter} intercepts AJAX requests made by a web
page, and extracts information from those requests. A programmer writes
a function which specifies how to extract data from an AJAX request, and
the framework handles the details of actually intercepting requests and
calling the programmer-defined function.

The \textbf{local storage adapter} simply stores a table of data in the
browser.

@@

We have designed the table adapter API to be general enough to
additional types of functionality in the future. Here are three concrete
examples of hypothetical possibilities:

\textbf{Integrated website adapters}: A key benefit of the table adapter
abstraction is that Wildcard is not coupled to web scraping as the only
means for integrating with existing sites, but can also accommodate
first party developers adding support directly into their own websites.
A DOM Scraping table adapter could be swapped out for such an
``integrated website adapter,'' which implements the exact same
interface as a scraping adapter but by directly accessing the internal
state of the user interface, without needing any scraping logic.

We think it is possible to create such adapters for existing frontend
web frameworks which result in minimal effort on the part of the
application developers. For example, we have created an initial
prototype of a plugin for the Redux state management library. Redux
implements the Model-View-Update pattern, which represents the entire
state of a user interface as a single centralized object. To configure
an integrated website adapter for such an existing application, the user
can simply specify a function projecting the centralized application
state as a table, and define handlers for how data edits to the table
should affect the state.

\textbf{Shared storage adapter}: It would be useful to share user
annotations between people and across devices---for example,
collaboratively taking notes with friends on a list of options for
places to stay on Airbnb. The existing Local Storage Adapter could be
extended to share live synchronized data with other users. This could be
achieved through a centralized web server (perhaps an existing service
like Google Sheets capable of storing tabular data), or through P2P
connections which might improve the privacy guarantees available for the
shared annotations.

\textbf{Third party API data adapter}: Currently, the main mechanism for
including data from web APIs in Wildcard is using spreadsheet formulas.
However, a web API could also be wrapped to expose a table API that
would dynamically create tables in response to queries. For example,
when fetching walkability scores for many GPS locations, the query
engine could request a table of walkability scores for various pairs of
latitude and longitude, and the table adapter could dynamically perform
API queries to populate a result table. (\emph{todo: why is this better
than spreadsheet formulas? I don't think it offers any more room for
batching performance optimization because we've already framed formulas
as whole-column, not row specific})

@@

To determine the viability of writing DOM scraping adapters, we built
adapters for 10 websites, including transactional sites like Amazon and
Uber Eats, media consumption sites like Hacker News and Youtube, and a
medical results entry platform managed by a member of our research
group. The adapters ranged from 36 to 117 lines of code, averaging 68
lines. In addition, an external developer unaffiliated with the project
contributed one adapter, designed to sort the Github page listing a
user's repositories, and described the experience as ``very
straightforward.''

\hypertarget{sec:discussion}{%
\section{Discussion}\label{sec:discussion}}

@@

There have been many attempts at simplifying aspects of traditional
programming to enable non-programmer end users to perform customization.
End user scripting languages (AppleScript, VBA, Chickenfoot, CoScripter)
have innovated at the syntax level, aiming to improve ease-of-use.
Visual programming environments (Mac Automator, Zapier) go further by
eliminating text syntax entirely, but maintain the same computational
model. Programming-by-demonstration and macro recording environments
(Applescript, Helena, WebVCR) remove some of the initial programming
burden by starting with concrete demonstrations, but typically require
programming later in the process.

However, all of these approaches share something in common: \textbf{an
imperative programming model}. They all involve a list of commands
executed in sequence, with control flow constructs like conditionals and
loops, and mutable variables. This makes some intuitive sense: many
customizations seem most naturally expressed as a series of commands,
each of which has a side effect on the UI: first enter this value, then
click this button, etc. The result is that end users eventually need to
become familiar with all of these traditional imperative programming
constructs, even if only in diluted form. (todo: bolster the case that
this is a barrier to learning)

Imperative programming is not the only possible model. Spreadsheets have
demonstrated another computational model: data editing via direct
manipulation, combined with pure functional expressions for computation,
with automatic reactive updates provided by the runtime. We call this a
data-oriented model, because the user is focused on editing data values
and producing the correct derived data values, rather than encoding a
sequence of commands. The success of spreadsheets with end user
programmers suggests that finding a way to apply data-oriented
programming model to software customization might enable more people to
modify their software. However, it's not immediately obvious how the
spreadsheet paradigm applies to customization.

A key insight from our work is that, rather than representing
customization as a series of commands issued to an existing application,
we can present a projected view of the application's internal state, and
let the user directly edit that projection as a means of customizing the
application. In some sense, this is similar to the DOM inspector, which
provides a user with an alternate representation of the UI that they can
directly manipulate (e.g., by selecting an element and deleting it from
the DOM tree). But rather than provide a low-level view of the user
interface elements, we instead provide a higher-level view of the
semantic state of the application.

Add here:

\begin{itemize}
\tightlist
\item
  multiple representations \citep{ainsworth1999}
\item
  address Tchernavskij's point about contrasting with instrumental
  interaction
\end{itemize}

@@

(\emph{Footnote this paragraph?}) This categorization is slightly
oversimplified, and there are existing customization ecosystems that
span both categories. For example, part of the success of browser
extensions stems from the fact that the DOM encourages the use of
standardized semantic UI elements; even if an app developer doesn't
anticipate customization, merely using of semantic and accessible HTML
creates a collateral benefit of easier extension. Another example of a
middle ground is AppleScript, which provides system-wide low-level APIs
for manipulating GUIs as a means of black-box customization, while also
enabling developers to optionally add application-specific APIs to add
support for semantic customization.

With Wildcard, we use a hybrid approach that takes the best of both
worlds. Programmers implement an API wrapper that is internally
implemented as a black-box customization, but externally provides a
semantic interface to the application. End users get an ergonomic and
simplified customization experience, but without the need to depend on a
first-party application developer exposing extension APIs.

One way to view this approach is as introducing a new abstraction
barrier into black-box extension. Typically, a black box customization
script combines two responsibilities: 1) mapping the low-level details
of a user interface to semantic constructs (e.g., using CSS selectors to
find certain page elements), and 2) the actual logic of the specific
customization. (todo: could easily show examples of this from browser
extensions, Chickenfoot, etc) Even though the mapping logic is often
more generic than the specific customization (e.g., finding a given
input element is independent of what text to insert into that element),
the intertwining of these two responsibilities in a single script makes
it very difficult to share the mapping logic across scripts. With
Wildcard we propose a decoupling of these two layers: a
community-maintained mapping layer, shared across many specific
customizations by individual users. This architecture has been
successfully used by projects like Gmail.js, an open source project that
creates a convenient API for browser extensions to interface with the
Gmail web email client.

Originally came from \citep{maclean1990}

\begin{itemize}
\tightlist
\item
  here's where ``automation vs customization'' comes in: automation
  frames it as entering a whole new scripting environment; we frame it
  more as just an alternate UI that you can use.
\item
  this is the heart of the gentle slope
\item
  backend APIs: terrible
\item
  the best would be right inline with the GUI (cite Scotty, instrumental
  work) but this has its own problems
\item
  we settle for a compromise: an alternate structured view. (explicitly
  contrast this clearly)
\item
  the CLI GUI thing
\end{itemize}

>>>>

We have known for decades about an alternate approach: \emph{direct
manipulation} \citep{shneiderman1983}, where ``visibility of the object
of interest'' replaces ``complex command language syntax''. Direct
manipulation is the de facto standard in GUIs today, but when it comes
to customizing software, it is rarely to be found. In this work, we ask:
what would it look like to build a software customization interface that
relies on direct manipulation? We take inspiration from spreadsheets and
visual database query interfaces \citep{2020a, bakke2016}, which have
successfully enabled end users to run queries and computations through
direct manipulation of data.

In this paper we present a technique called \emph{table-driven
customization} which applies these ideas from visual query interfaces in
the context of software customization. We augment an application's UI
with a table view, where the user can see and manipulate the structured
data inside an application. Changes in the table view result in
immediate corresponding changes to the original user interface of the
application, enabling the user to customize an application with live
feedback.

We have developed a browser extension called Wildcard which uses web
scraping techniques to implement table-driven customization for existing
Web applications. In Section~\ref{sec:examples} we concretely introduce
the key ideas of table-driven customization by presenting several
examples of real customizations implemented in Wildcard.

In Section~\ref{sec:architecture} we explain the architecture of
table-driven customization. We focus on the \emph{table adapter}
abstraction, which allows many different types of underlying state to be
bidirectionally mapped to a table of data. We describe certain types of
table adapters we've built in Wildcard; we also describe future adapters
that could be supported in the general paradigm.

We have used Wildcard to build real customizations for 11 different
websites. In Section~\ref{sec:evaluation} we present reflections from
this process: customizations we were able to build, limitations we
encountered, and reflections on the ease of integrating scraping logic
with real websites.

Table-driven customization embodies several design principles for
building customizable software systems, discussed in
Section~\ref{sec:themes}:

@@

\emph{todo: maybe redo this as a separate example to avoid self
plagiarism?}

@@

@@

Figure~\ref{fig:table-adapter} summarizes the overall architecture of
table-driven customization, using a simplified version of the Airbnb
example above. In this example, the name of each listing is scraped from
the web page DOM, the latitude and longitude of each listing is scraped
from AJAX responses, and user annotations are loaded from the brower's
local storage.

First, the three different data sources are each bidirectionally mapped
to a table interface by a \textbf{table adapter}. The table adapter
defines how to map a particular type of data to a table, and what
effects edits should have on the original data source. In some cases,
the mapping logic is straightforward: the local storage adapter stores a
table of data, so the mapping to the table abstraction is trivial. In
other cases, the mapping is more involved: the DOM scraping adapter
implements web scraping logic to produce a table of data from the web
page, and edits to the table result in DOM manipulations like reordering
rows of data on the page.

Ultimately, we provide the user with a single combined table view that
they can edit, rather than three separate tables. The \textbf{query
engine} is responsible for combining the tables of data into this single
view, and routing the user's edits back to the individual table
adapters. In this example, the query engine has joined the three tables
together by a shared ID column, and sorted the result by the name
column.

We now examine each component of the system in more detail.

@@

A key idea in table-driven customization is that different data sources
can all be mapped to the generic abstraction of an editable table. In a
relational database, the table matches the underlying storage format,
but in table-driven customization, the table is merely an
\emph{interface layer}. The data shown in the table is a projection of
some underlying state, and edits to the table can have arbitrary effects
on the underlying state.

Externally, a table adapter must satisfy an abstract interface. The
first two parts of the interface largely resemble the interface exposed
by a table in a relational database:

\textbf{Returning a table}: A table adapter exposes a table of data: an
ordered list of records. Each record contains associates attributes and
values. Tables have a typed schema, so the same attributes are shared
across all records. A table adapter can update the contents of a table
at any time, in response to changes in the underlying state (e.g., a DOM
scraping adapter can update the table when the page body changes). New
data is pushed out to other components of the system, and the query view
reactively updates in response.

\textbf{Making edits}: The query engine can request to a table adapter
to make an edit to a record. The meaning of making an edit can vary
depending on the adapter: in the local storage adapter, an annotation
can be persisted into local storage; in the DOM scraping adapter, an
edit can represent filling in a form field. An adapter can also mark
values as read-only if it wouldn't be meaningful to edit them; for
example, the DOM scraping adapter typically marks page content as
read-only, except for editable form fields.

The query engine also sends additional information about the combined
query view to each table adapter. These functions are currently used to
provide the DOM scraping adapter with sufficient information to
manipulate the original application UI as the user manipulates the table
view.

\textbf{Sorting/filtering}: When the user sorts or filters the query
view, an ordered list of visible IDs is sent to each table adapter. The
DOM scraping adapter uses this information to modify the list of visible
rows in the web page.

\textbf{Information from other tables}: The query engine sends each
table adapter the entire combined table of data being rendered to the
user. The DOM scraping adapter uses this to add annotations to the page
by looking for additional data columns joined to scraped rows, and
rendering them in the page.

\textbf{Currently selected record}: The query engine notifies each table
adapter about which record is currently selected by the user in the
table UI. The DOM scraping adapter uses this information to highlight
the row in the page that corresponds to the selected record in the
table.

\hypertarget{types-of-table-adapters}{%
\subsubsection{Types of table adapters}\label{types-of-table-adapters}}

Here we describe in more detail the table adapters which we have
implemented in Wildcard to power the customizations shown in
Section~\ref{sec:examples}.

\textbf{DOM scraping adapters} are the essential component that enables
Wildcard to interface with an existing website UI. In addition to the
standard web scraping problem of extracting a table of data from the
DOM, a scraping adapter must also manipulate the DOM to re-order rows,
edit form entries, and inject annotations as the table is edited.

Because each website has unique content, we rely on programmers to
create a DOM scraping adapter for each individual website to make it
available for customization in Wildcard. To make this approach viable,
we have built library functions that make it as easy as possible to
implement a scraping adapter, only requiring the programmer to implement
the minimal site-specific parts. The programmer writes a single scraping
function which uses CSS selectors and DOM APIs to extract and return
relevant elements from the page. The library functions then wrap this
function to implement the rest of the needed functionality; for example,
when the table is sorted, we find the DOM elements corresponding to the
rows in the table, remove them from the page, and then reinsert them in
the new order.

An \textbf{AJAX scraping adapter} intercepts AJAX requests made by a web
page, and extracts information from those requests. When available, this
tends to be a helpful technique because the data is already in a
structured form, and often includes information not shown in the UI. As
with DOM scraping adapters, we have made it as easy as possible for
programmers to create site-specific AJAX scraping adapters. A programmer
writes a function which specifies how to extract data from an AJAX
request, and the framework handles the details of actually intercepting
requests and calling the programmer-defined function.\footnote{So far we
  have only implemented AJAX scraping in the Firefox version of
  Wildcard, since Firefox has convenient APIs for intercepting requests.
  It appears possible to implement in Chrome as well, but we have not
  finished our implementation.}

The \textbf{local storage adapter} simply stores a table of data in the
browser. As shown in the example use cases, this can be useful for
privately persisting annotations, without needing to upload them to a
web service.

@@

We have designed the table adapter API to be general enough to support
other types of useful adapters in the future. Here are three examples of
future possibilities:

\textbf{Integrated website adapters}: A key benefit of the table adapter
abstraction is that Wildcard is not coupled to web scraping as the only
means for integrating with existing sites, but can also accommodate
first party developers adding support directly into their own websites.
A DOM Scraping table adapter could be swapped out for an ``integrated
website adapter'' which directly accesses the internal state of the
application, without needing to extract it from the UI.

With the advent of rich frontend web frameworks, structured application
state is now often available in the web client. We suspect it is
possible to create plugins for frontend frameworks which expose
structured state to Wildcard with minimal effort from the application
developers. For example, we have created an initial prototype of a
plugin for the Redux state management library, which represents the
state of a user interface as a single object. To configure an integrated
website adapter for such an existing application, the user simply
specifies two functions. The first one projects the centralized
application state into a table, and define handlers for how data edits
to the table should affect the state.

\textbf{Shared storage adapter}: It would be useful to share user
annotations between people and across devices---for example,
collaboratively taking notes with friends on a list of options for
places to stay on Airbnb. The existing Local Storage Adapter could be
extended to share live synchronized data with other users. This could be
achieved through a centralized web server, or through P2P connections
which might provide stronger privacy guarantees.

\textbf{Third party API data adapter}: Currently, the main mechanism for
including data from web APIs in Wildcard is using spreadsheet formulas.
However, a web API could also be wrapped to expose a table API that
would dynamically create tables in response to queries. For example,
when fetching walkability scores for many GPS locations, the query
engine could request a table of walkability scores for various pairs of
latitude and longitude, and the table adapter could dynamically perform
API queries to populate a result table. (\emph{todo: make a stronger
case for why this is useful or better than formulas})

(\emph{note: another ordering for the adapters could be by function.
First, DOM, AJAX, and Redux, which all integrate with the original app.
Then, Local Storage, Shared Storage, API, which are all about adding
functionality to the site. This might make more logical sense, but it
risks confusing what's already been done and what's a future
possibility. The current order seems good enough?})

@@

\hypertarget{sec:themes}{%
\section{Key themes}\label{sec:themes}}

@@

\begin{itemize}
\tightlist
\item
  reprise intro--explain direct manipulation
\item
  the key is that the DATA is being direct manipulated, not a script
\item
  it's essentially an alternate UI for an existing app, not a scripting
  env
\item
  argue for the benefit of multiple representations
  \citep{ainsworth1999}

  \begin{itemize}
  \tightlist
  \item
    abstraction
  \item
    different affordances
  \end{itemize}
\item
  address Tchernavskij's point about contrasting with instrumental
  interaction
\end{itemize}

Term originally came from \citep{maclean1990}

\begin{itemize}
\tightlist
\item
  \citep{maclean1990} says ``some customizations should be as easy as
  using the app'', we have achieved that
\item
  here's where ``automation vs customization'' comes in: automation
  frames it as entering a whole new scripting environment; we frame it
  more as just an alternate UI that you can use.
\item
  backend APIs: terrible
\item
  the best would be right inline with the GUI (cite Scotty, instrumental
  work) but this has its own problems
\item
  we settle for a compromise: an alternate structured view. (explicitly
  contrast this clearly)
\item
  the CLI GUI thing
\end{itemize}

@@

With Wildcard, we use a hybrid approach that takes the best of both
worlds. Programmers implement an API wrapper that is internally
implemented as a black-box customization, but externally provides a
semantic interface to the application. These wrappers are added to a
shared repository, available to all users of the system. When an end
user is using a site that already has an adapter, they get a semantic
customization experience that avoids low-level details.

One way to view this approach is as introducing a new abstraction
barrier into third-party extension. Typically, a third party
customization script combines two responsibilities: 1) mapping the
low-level details of a user interface to semantic constructs (e.g.,
using CSS selectors to find certain page elements), and 2) the actual
logic of the specific customization. (todo: could easily show examples
of this from browser extensions, Chickenfoot, etc) Even though the
mapping logic is often more generic than the specific customization, the
intertwining of these two responsibilities in a single script makes it
very difficult to share the mapping logic across scripts.

With Wildcard we propose a decoupling of these two layers: a
community-maintained mapping layer, shared across many specific
customizations by individual users. This architecture has been
successfully used by projects like Gmail.js, an open source project that
creates a convenient API for browser extensions to interface with the
Gmail web email client.

We have used Wildcard to build customizations for many real websites. So
far, most usage has come from members of the project team, although we
have had a few external users try the system. Here we offer our
reflections on using the system, focused on two key questions:

\begin{itemize}
\tightlist
\item
  What is the range of useful customizations possible in this paradigm?
\item
  How feasible is it to build DOM scraping adapters for real websites,
  in practice?
\end{itemize}

\hypertarget{range-of-customizations}{%
\subsection{Range of customizations}\label{range-of-customizations}}

\emph{todo}

\hypertarget{viability-of-dom-scraping}{%
\subsection{Viability of DOM scraping}\label{viability-of-dom-scraping}}

In order for our idea of third-party customization through Wildcard to
succeed, it is important that creating usable adapters for existing
websites takes minimal effort.

To test the viability of writing DOM scraping adapters, we built
adapters for 10 websites, including transactional sites like Amazon and
Uber Eats, media consumption sites like Hacker News and Youtube, and a
medical results entry platform managed by a member of our research
group. The adapters ranged from 36 to 117 lines of code, averaging 68
lines. In addition, an external developer unaffiliated with the project
contributed one adapter, designed to sort the Github page listing a
user's repositories, and described the experience as ``very
straightforward.''
